mathml: Translate R expressions to MathML and LaTeX/MathJax

### 2023-01-10 rj/mathml.Rmd
case study gof

op3 <- list(
  twosidearrow=quote(A %<->% B),
  rightarrow=quote(A %->% B),
  leftarrow=quote(A %<-% B),
  uparrow=quote(A %up% B),
  down=quote(A %down% B),
  iff=quote(A %<=>% B),
  rArr=quote(A %=>% B),
  lArr=quote(A %<=% B),
  dblup=quote(A %dblup% B),
  dbldown=quote(A %dbldown% B))

@@

The overall goodness-of-fit is the sum of the squared \(z\)-statistics for each
onset asynchrony. Assuming again that the architecture of the model is correct,
but the parameters are adjusted to the data, it follows
a \(\chi^2(8~\mathrm{df})\)-distribution. The degrees of freedom result from
the 13 predicted mean response times, minus 5 free parameters.

$X^2=\Sigma_\tau z^2_\tau \sim\chi^2(13-5\ df)$.

```{r, results='asis'}
gof <- function(par, tau, m, s, n)
{
  zn <- Vectorize(z, vectorize.args='tau')
  zi <- zn(m, s, n, tau, c=100L, mu_A=par["mu_A"], sigma_A=par["sigma_A"], mu_B=par["mu_B"], sigma_B=par["sigma_B"], mu_M=par["mu_M"])
  sum(zi^2L)
}

mathout(gof)
```

>>>>

op3 <- list(
  twosidearrow=quote(A %<->% B),
  rightarrow=quote(A %->% B),
  leftarrow=quote(A %<-% B),
  uparrow=quote(A %up% B),
  down=quote(A %down% B),
  iff=quote(A %<=>% B),
  rArr=quote(A %=>% B),
  lArr=quote(A %<=% B),
  dblup=quote(A %dblup% B),
  dbldown=quote(A %dbldown% B),
  " "="")

@@

The overall goodness-of-fit is the sum of the squared \(z\)-statistics for each
onset asynchrony. Assuming again that the architecture of the model is correct,
but the parameters are adjusted to the data, it follows
a \(\chi^2(8~\mathrm{df})\)-distribution.

```{r, results='asis'}
zv <- Vectorize(z, vectorize.args='tau')

hook(call("zv", expression(m), expression(s), expression(n), expression(tau), 
        expression(c), expression(mu_A), expression(sigma_A), expression(mu_B), expression(sigma_B), expression(mu_M)), quote(z[tau]))

gof <- function(par, tau, m, s, n)
  sum(zv(m, s, n, tau, c=100L, mu_A=par["mu_A"], sigma_A=par["sigma_A"], 
         mu_B=par["mu_B"], sigma_B=par["sigma_B"], mu_M=par["mu_M"])^2L)

mathout(call("=", quote(X["8 df"]^2L), gof))
```

The degrees of freedom result from the 13 predicted mean response times,
minus 5 free parameters (\(c\) is a redundant scaling parameter).
